Adaptive Hierarchical Sliding Mode Control with Input Saturation for Attitude Regulation of Multi-satellite Tethered System

### 2016-07-04 manuscript.tex
20160704

\begin{abstract}
This paper proposes  a  novel adaptive hierarchical  sliding mode control for the attitude regulation of the multi-satellite inline tethered system, where the input saturation is taken into account. The governing equations for the attitude dynamics of the three-satellite inline tethered system are derived firstly by utilizing Lagrangian mechanics theory. Considering the fact that the attitude of the central satellite can be adjusted by using the simple exponential stabilization scheme, the decoupling of the central satellite and the terminal ones is presented, and in addition, the new adaptive sliding mode control law is applied to stabilize the attitude dynamics of the two terminal satellites based on the synchronization and partial contraction theory. In the adaptive hierarchical sliding mode control design, the input is modeled as saturated input due to the fact that the flywheel torque is bounded, and meanwhile, an adaptive update rate is introduced to eliminate the effect of the saturated input and the external perturbation. The proposed control scheme can be applied on the two-satellite system to achieve fixed-point rotation. Numerical results validate the effectiveness of the proposed method.
\keywords{Multi-satellite tethered system \and Adaptive Sliding mode \and Input saturation \and Satellite attitude adjusting \and Underactuated system stabilization}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

The issue about attitude regulation of the three-satellite inline tethered system is converted into designing the independent control system for the individual satellite described as Eq.~(\ref{eq:model}), and meanwhile, the system is strict saturated, coupled and nonlinear. There exists a stable hierarchical sliding mode approach (HSM) investigated for a class of second order underactuated systems, like Acrobot, overhead crane and pendubot etc~\cite{wang2004design}, and the state space equations of the these models are similar to the form of Eq.~(\ref{eq:model}). Considering the effect of the input saturation, synthesizing the HSM and adaptive sliding mode control schemes derives a modified method, which can overcome both the input saturation and coupling characteristics.\par

@@

For voiding the singularity of the input~(\ref{eq:u}), the selection of $\alpha$ and $\beta$ may satisfy the condition: $\alpha=\beta>0$. One can check that $\alpha b_1(X,t)+\beta b_2(X,t)$ is positive to get non-singular the input,

@@

    \alpha b_1(X,t)+\beta b_2(X,t) &= \alpha(b_1(X,t)+b_2(X,t))\\
    &=\frac{\alpha(-mrl\cos x_3+mrl\cos x_3+ml^2)}{I_rml^2-m^2r^2l^2\cos{^2x_3}}\\
    &=\frac{\alpha ml^2}{I_rml^2-m^2r^2l^2\cos{^2x_3}}>0.

@@

    Moreover, according to the derivation above, selecting $\alpha$ and $\beta$ with $\beta>\alpha>0$ yields 
    \alpha b_1(X,t)+\beta b_2(X,t) &= \alpha(b_1(X,t)+b_2(X,t))+(\beta-\alpha)b_2(X,t)\\
    &=\frac{(\beta-\alpha)mrl\cos x_3 + \beta ml^2}{I_rml^2-m^2r^2l^2\cos{^2x_3}}>0.
    This can also guarantee the non-singularity of Eq.~(\ref{eq:u}), because $x_3$ should be varying in a small region with $\vert x_3\vert<\pi/2$.

@@

I_rml^2(2I_r-mr^2\cos{^2\phi_1}-mr^2\cos{^2\phi_2})
&= I_rml^2(2I_g+2mr^2-mr^2\cos{^2\phi_1}-mr^2\cos{^2\phi_2})\\
&= I_rml^2[2I_g+mr^2(1-\cos{^2\phi_1})+mr^2(1-\cos{^2\phi_2})]>0

@@

For voiding the singularity of the inputs, the parameter $\bar\alpha$, $\bar\beta$ and $\bar\iota$ should satisfy the the condition $\bar\alpha=\bar\beta=\bar\iota>0$. Consider the denominator of the input $u_1$:

@@

    &\bar\alpha b_1(X,t) + \bar\beta b_3(X,t) + \bar\iota b_5(X,t)\\
    =&\bar\alpha(b_1(X,t) + b_3(X,t) + b_5(X,t))\\
    =&\bar\alpha(2ml^2I_r-m^2r^2l^2\cos^2\phi_2+I_rmrl\cos\phi_1+m^2r^2l^2\cos\phi_2\cos\phi_1)\\
    =&\bar\alpha(ml^I_r+ml^2I_g+m^2r^2l^2(1-\cos^2\phi_2)+I_rmrl\cos\phi_1+m^2r^2l^2\cos\phi_2\cos\phi_1)

@@

    where $\vert\phi_1\vert<\pi/2$ and $\vert\phi_2\vert<\pi/2$, and hence $\bar\alpha b_1(X,t) + \bar\beta b_3(X,t) + \bar\iota b_5(X,t)>0$. Also, $\bar\alpha b_2(X,t) + \bar\beta b_4(X,t) + \bar\iota b_6(X,t)>0$ can be obtained with the same derivation.

@@

Referring to the experiment of SPHERES project, the simulation parameters describing the physical characteristics of the satellite are listed in Table~\ref{tab:1}. According to the parameter list, the input boundary is determined as $T_p = -T_n = 0.207Nm$. In particular the controller's output is programmed to satisfy the restriction of the actuator, which can avoid the block of the flywheels in some extent. The length of the tether is constant, since the variety of the length rate leads to an extremely complicated and unstable multi-satellite tethered systems. The reasonable length of the tether is essential, $l = 0.9m$, $\dot{l}=0m/s$, although the length will not take an important role in the following process of validating. In this simulation, it is assumed that the satellites expose itself to the real space environment, and there exist the solar radiation pressure torque and aerodynamic torque effecting its attitude stability. The values of the perturbation torques are approximate to $1\times 10^{-5}Nm$ on account of the researches on perturbation in space, and hence the external perturbation term can be expressed by a sinusoidal function whose amplitude equals to the boundary of perturbations~\cite{liu2013calculation}. Since the relative distance among the participating satellites is not large, without loss of generality, the form of preceding perturbation is identical.

@@

d_i(X,t) \approx 1\times 10^{-5}\sin{(0.01\pi t)}\notag

>>>>

\begin{abstract}
This paper proposes  a  novel adaptive \begin{color}{red}hierarchical\end{color}  sliding mode control for the attitude regulation of the multi-satellite inline tethered system, where the input saturation is taken into account. The governing equations for the attitude dynamics of the three-satellite inline tethered system are derived firstly by utilizing Lagrangian mechanics theory. Considering the fact that the attitude of the central satellite can be adjusted by using the simple exponential stabilization scheme, the decoupling of the central satellite and the terminal ones is presented, and in addition, the new adaptive sliding mode control law is applied to stabilize the attitude dynamics of the two terminal satellites based on the synchronization and partial contraction theory. In the adaptive hierarchical sliding mode control design, the input is modeled as saturated input due to the fact that the flywheel torque is bounded, and meanwhile, an adaptive update rate is introduced to eliminate the effect of the saturated input and the external perturbation. The proposed control scheme can be applied on the two-satellite system to achieve fixed-point rotation. Numerical results validate the effectiveness of the proposed method.
\keywords{Multi-satellite tethered system \and Adaptive Sliding mode \and Input saturation \and Satellite attitude adjusting \and Underactuated system stabilization}
% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

The issue about attitude regulation of the three-satellite inline tethered system is converted into designing the independent control system for the individual satellite described as Eq.~(\ref{eq:model}), and meanwhile, the system is strict saturated, coupled and nonlinear. There exists a stable \begin{color}{red}hierarchical sliding mode (HSM)\end{color} approach investigated for a class of second order underactuated systems, like Acrobot, overhead crane and pendubot etc~\cite{wang2004design}, and the state space equations of the these models are similar to the form of Eq.~(\ref{eq:model}). Considering the effect of the input saturation, synthesizing the HSM and adaptive sliding mode control schemes derives a modified method, which can overcome both the input saturation and coupling characteristics.\par

@@

For voiding the singularity of the input~(\ref{eq:u}), the selection of $\alpha$ and $\beta$ may satisfy the condition: $0<\alpha\le\beta$.
    Selecting $\alpha$ and $\beta$ with $0<\alpha\le\beta$ yields

@@

    &\alpha b_1(X,t)+\beta b_2(X,t)\\
    =& \alpha(b_1(X,t)+b_2(X,t))+(\beta-\alpha)b_2(X,t)\\
    =&\frac{(\beta-\alpha)mrl\cos x_3 + \beta ml^2}{I_rml^2-m^2r^2l^2\cos{^2x_3}}>0.

@@

    This can guarantee the non-singularity of Eq.~(\ref{eq:u}), because $x_3$ should be varying in a small region with $\vert x_3\vert<\pi/2$.

@@

&I_rml^2(2I_r-mr^2\cos{^2\phi_1}-mr^2\cos{^2\phi_2})\\
=& I_rml^2(2I_g+2mr^2-mr^2\cos{^2\phi_1}-mr^2\cos{^2\phi_2})\\
=& I_rml^2[2I_g+mr^2(1-\cos{^2\phi_1})+mr^2(1-\cos{^2\phi_2})]>0

@@

For voiding the singularity of the input, the parameter $\bar\alpha$, $\bar\beta$ and $\bar\iota$ should satisfy the the condition $0<\bar\alpha\le\bar\iota$ and $0<\bar\alpha\le\bar\beta$.\par
    Consider the expression $\bar\alpha b_1(X,t) + \bar\beta b_3(X,t)$ with $0<\bar\alpha\le \bar\beta$

@@

    &\bar\alpha b_1(X,t) + \bar\beta b_3(X,t)\\
    =&-\bar\alpha I_rmrl\cos\phi_1 + \bar\beta I_rmrl\cos\phi_1+\bar\beta[ml^I_r+ml^2I_g+m^2r^2l^2(1-\cos^2\phi_2)]\\
    =&(\bar\beta-\bar\alpha) I_rmrl\cos\phi_1+\bar\beta[ml^I_r+ml^2I_g+m^2r^2l^2(1-\cos^2\phi_2)]>0

@@

    where $\vert\phi_1\vert<\pi/2$ and $\vert\phi_2\vert<\pi/2$.
    In addition, it is obvious that $b_5(X,t)>0$, and hence, for voiding the singularity of $\bar\alpha b_1(X,t) + \bar\beta b_3(X,t) + \bar\iota b_5(X,t)$,  the parameters should satisfy the condition $0<\bar\alpha\le\bar\beta$ and $\bar\iota>0$. $\bar\alpha b_2(X,t) + \bar\beta b_4(X,t) + \bar\iota b_6(X,t)>0$ can be obtained under the condition: $0<\bar\alpha\le\bar\iota$ and $\bar\beta>0$. Conclusively, $0<\bar\alpha\le\bar\iota$ and $0<\bar\alpha\le\bar\beta$ guarantee the non-singularity of the input in the MHSM control.

@@

Referring to the experiment of SPHERES project, the simulation parameters describing the physical characteristics of the satellite are listed in Table~\ref{tab:1}. According to the parameter list, the input boundary is determined as $T_p = -T_n = 0.207Nm$. In particular the controller's output is programmed to satisfy the restriction of the actuator, which can avoid the block of the flywheels in some extent. The length of the tether is constant, since the variety of the length rate leads to an extremely complicated and unstable multi-satellite tethered systems. The reasonable length of the tether is essential, $l = 0.9m$, $\dot{l}=0m/s$, although the length will not take an important role in the following process of validating. In this simulation, it is assumed that the satellites expose itself to the real space environment, and there exist the solar radiation pressure torque and aerodynamic torque effecting its attitude stability. The values of the perturbation torques are approximate to $1\times 10^{-5}Nm$ on account of the researches on perturbation in space, and hence the external perturbation term can be expressed by a sinusoidal function whose amplitude equals to the boundary of perturbations~\cite{liu2013calculation}. \begin{color}{red}Without loss of generality, the perturbation term is thought to be a periodic function, and the period is $5000s$ approximately, which equals to the orbital period~\cite{inamori2015magnetic}. Hence for verifying the effectiveness of the MHSM control, the satellite is exerted by a sinusoidal perturbation whose amplitude is no more than $1\times 10^{-5}Nm$ with $2\times 10^{-4}Hz$. Since the relative distance among the participating satellites is not large, without loss of generality, the form of preceding perturbation is identical.

@@

d_i(X,t) \approx 2\times 10^{-5}\sin(2\pi/5000)\notag
